This page and the next page should be removed

### 2021-04-20 analysis/manuscript.Rmd
compute maximal freq models

```{r exp1-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> aha

@@

# Define formula and parameters for linear mixed-effects regression models (LMMs)
formula_exp12 <- buildmer::tabulate.formula(
  ~ part * condition + (part * condition | participant) + (part * condition | item)
) %>% mutate(block = replace(block, is.na(grouping), "fixed"))
control <- lme4::lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Define formula for follow-up contrasts
specs_exp12 <- pairwise ~ condition | part

# Define function to compute LMMs and follow-up contrasts for each component
compute_models <- function(dep, formula, data, control, specs) {
  require(lmerTest)
  require(buildmer)
  require(emmeans)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  build <- buildmer(
    control = control,
    REML = FALSE,
    buildmerControl = buildmerControl(
      formula = formula,
      data = data,
      direction = c("backward", "backward"),
      elim = function(logp) exp(logp) >= .20,
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans
  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts
  modlist <- list(
    model = build@model,
    anova = build@anova,
    summary = build@summary,
    means = means %>% as.data.frame(),
    contrasts = conts %>% as.data.frame()
  )
  return(modlist)
}

# Compute the models for Experiment 1
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = aha,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
```

>>>>

```{r exp1-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/aha-trials.csv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> aha

@@

# Specify model formula and follow-up contrasts
form <- erp ~ part * condition +
  (part * condition | participant) +
  (part * condition | item)
specs <- pairwise ~ condition | part

# Calculate linear mixed-effects models and contrasts
map(comps$name, function(comp, formula = form, data = aha, specs = specs) {
  require(afex)
  require(emmeans)
  data %<>% rename(erp = all_of(comp))
  mod <- mixed(
    formula,
    data,
    method = "S",
    check_contrasts = FALSE,
    all_fit = TRUE
  )
  em <- emmeans(mod, specs = specs, infer = TRUE, data = data)
  modlist <- list(
    model = mod,
    anova = anova(mod),
    summary = summary(mod),
    means = as.data.frame(em$means),
    contrasts = as.data.frame(em$contrasts)
  )
}) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/aha_models_freq.RDS") -> mods_freq
```
